A Comparison of Graph Processing Systems

### 2020-09-22 documentation/paper/sections/introduction.tex
Rest der Introduction schlecht ausformuliert

Some frameworks were developed for this purpose.
One of the best known is the closed source distributed graph processing system Pregel \cite{pregel}.
Pregel, as well as some open source versions of it, like Giraph \cite{Giraph} and GraphX \cite{graphx}, was built to handle large graphs reliable and fault tolerant on large MapReduce infrastructures.
Due to the lack of cache locality, as these systems are written object oriented, they provide rather suboptimal performance.
Because of this, some non-uniform memory access (NUMA) aware systems like Ligra \cite{Ligra}, Polymer \cite{Polymer}, Galois \cite{Galois} and Gemini \cite{Gemini} were introduced.
\\
- Prolem der Vergleichbarkeit der Systeme\\
- Systeme entwickeln sich weiter und wurden nur zu deren Start verglichen\\
- Vergleiche wurden von Machern der Systeme erledigt\\
\\
3. Was wir zur Lösung des Problems beitragen\\
- ersten, die unabhängig alle Systeme Vergleichen 2020\\
- Wir vergleichen die Frameworks nach folgenden Gesichtspunkten:\\
(Benutzerfreundlichkeit, Performanz/Varianz, Weiterentwicklung)
- We compare several non-uniform memory access (NUMA) aware systems in terms of their performance on three graph algorithms (PageRank, SSSP, BFS).\\
- The comparison is performed on both real world data sets and synthetic graphs.
To provide a comparison to a non-NUMA aware system, Giraph\cite{Giraph} is included in the testing. Giraph itself has often been compared to other state of the art systems like Pregel or GraphX.
- Comparison of several state-of-the-art graph processing frameworks\\
\\

This paper makes the following contributions:
\begin{itemize}
  \item Comparison of several state-of-the-art graph processing frameworks
  \item
  \item
  \item
\end{itemize}

4. Wie ist das Paper aufgebaut\\
- Section 2: Relatet Work (Wie haben die Macher der Systeme die Systeme verglichen)\\
- Section 3: Preliminaries (Was muss man an technischen Details wissen)\\
- Section 4: Framework Overview (Welche Frameworks und was macht diese aus)\\
- Section 5: Evaluaten (Was wurde gemessen?, Wie wurde gemessen?, Was sind die Ergebnisse?)\\
- Section 6: Discussion (Warum sehen die Ergebnisse so aus, wie sie aussehen?)\\
- Section 7: Concluseion (Was lernen wir daraus?)\\

>>>>

Some frameworks were developed for this purpose.
One of the best known is the closed source distributed graph processing system Pregel \cite{pregel}.
Pregel, as well as some open source versions of it, like Giraph \cite{Giraph} and GraphX \cite{graphx}, was built to handle large graphs reliable and fault tolerant on large MapReduce infrastructures.
Due to the lack of cache locality, as these systems are written object oriented, they provide rather suboptimal performance.
Because of this, some non-uniform memory access (NUMA) aware systems like Ligra \cite{Ligra}, Polymer \cite{Polymer}, Galois \cite{Galois} and Gemini \cite{Gemini} were introduced.
These systems have some similarities, but many differences, which partly results in considerable performance differences.
The systems were compared at their proposal.
However, these comparisons were often incomplete, or are simply no longer relevant today, since most of the systems are several years old and some of them have evolved, or are still evolving.
Other systems are simply no longer used today, which also reduces the significance of the comparisons.

Therefore we compared several state-of-the-art non-uniform memory access (NUMA) aware systems in terms of their performance on three graph algorithms (PageRank, SSSP, BFS).
The comparison is performed on both real world data sets and synthetic graphs.
To provide a comparison to a non-NUMA aware system, Giraph is included in the testing.
Giraph itself has often been compared to other state-of-the-art systems like Pregel or GraphX.
We also included a comparison of Galois with itself with and without hugepages \cite{hugepages}, and several runs with different numbers of threads to see how it scales.
Where possible, several versions of the algorithms were used, like the push and pull variants.

The rest of this paper is organized as follows.
In section 2 we first clarify what a graph is, how the algorithms we are looking at work and what else is necessary for further understanding. Then we give a short overview of the graph formats we are looking at in section 3 and of the graph formats used in section 4. Before we come to our results, we show in section 5 what has been done in this area so far. In Section 6, which is the core of the paper, we will present all our results and also briefly show how they were developed. After that, in section 7, we will discuss these results. And at the end in section 8 we will present our conclusion.
